Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-17 main.tex
CP progress on basic definition
Notes for meeting

In particular, the observation $\obstrace(\seq{(\contour,\mach)})$ arising
from a contoured trace $\seq{(\contour,\mach)}$ is sequence of state
observations $\stateobs_0,\, \stateobs_1,\, \ldots$ defined informally as
follows:
\begin{itemize}
\item $\stateobs_0$ maps every visible component (where $\contour_0 = \VIS$)
to its value in $\mach_0$ and every hidden
component to $\bot$; 
\item $\stateobs_{i+1}$ is defined from $\stateobs_{i}$ by (1) for each
visible component (where $\contour_{i+1} = \VIS$), copying its
value from $\mach_{i+1}$, and (2) for each
hidden component, where $\contour_i = \VIS$, copying its
value from $\stateobs_{i+1}$, and (3) if the resulting $\stateobs_{i+1}$ is
identical to $\stateobs_{i}$, then skipping $\stateobs_{i+1}$.
\iftext\bcp{Too informal!!}\fi

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.

@@

>>>>

In particular, the observation $\obstrace(\seq{(\contour,\mach)})$ arising
from a contoured trace $\seq{(\contour,\mach)}$ is sequence of state
observations $\stateobs_0,\, \stateobs_1,\, \ldots$ defined informally as
follows:
\begin{itemize}
\item $\stateobs_0$ maps every visible component (where $\contour_0 = \VIS$)
to its value in $\mach_0$ and every hidden
component to $\bot$; 
\item $\stateobs_{i+1}$ is defined from $\stateobs_{i}$ by (1) for each
visible component (where $\contour_{i+1} = \VIS$), copying its
value from $\mach_{i+1}$, and (2) for each
hidden component, where $\contour_i = \VIS$, copying its
value from $\stateobs_{i+1}$, and (3) if the resulting $\stateobs_{i+1}$ is
identical to $\stateobs_{i}$, then skipping $\stateobs_{i+1}$.
\iftext\bcp{Too informal!!}\fi
\end{itemize}

@@

\leo{Low should be VIS here right?}
Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.

@@

\leo{Some notes for the meeting}

In traditional NI viewed as a pair of contoured traces $\overline{(C, M_i)}$ and
$\overline{(C, N_i)}$, we can have the following formulations:
\begin{enumerate}
\item $M_0, N_0 \in \mathit{Initial State}, ~\text{s.t.} ~\mathit{variant}(C, M_0, N_0)$
\item $M_0 \in \mathit{Initial State}, N_0 \in \mathit{Variant}(C, M_0)$
\item $M_0, N_0 \in \mathit{Reachable State}, ~\text{s.t.} ~\mathit{variant}(C, M_0, N_0)$
\item $M_0 \in \mathit{Reachable State}, N_0 \in \mathit{Variant}(C, M_0)$
\end{enumerate}
%
The (intuitive) top level property we care about is (1) - end to end
noninterference.
%
Property (2) is easier to test - but not always equivalent (if the set
of variants of an initial state can take you outside the set of
initial states).
%
Property (3) is also easier to test than - you start from an arbitrary
(reachable) state instead of an initial one, allowing to get to the
interesting part sooner.
%
Property (4) corresponds to what we actually want to test - start from
an arbitrary (reachable) state, vary it, test the trace.

As far as facilitating testing goes, the assumption of SSNI is that
you don't need to test full traces - you can test all traces of length
1 and that somehow gives you confidence for the full property.
%
More importantly, note that going from (1,2) to (3,4) doesn't really
change the property itself {\em as long as the contour stays identical
  throughout the execution}.

Now, when the contour does change the expressive power of (3,4) and (1,2)
is slightly different:
\begin{itemize}
\item If the contour C makes more things hidden at step $i$, then
  starting from the (reachable) state $M_i$ and taking its variant can
  lead to a pair $M_i, N_i$ that is not reachable from a pair of variant
  initial states.
\item If the contour C declassifies things at step $i$, then traces
  that started from variants $M_0, N_0$ based on a more restrictive
  contour C, can reach that point and no longer remain variant based
  on the new contour.
\end{itemize}
Therefore an additional property of the hyperproperties when
classification/declassification is involved, is that the traces
in the property start at some contour level C0 and are truncated
after C becomes more permissive than C0.

The stack property we test is just a way of testing such a
hyperproperty more efficiently.
